# R Script for creating a bibliometric dataframe using bibliometrix from WoS and Scopus and selecting only articles included in the Rayyan screening.

# Loading packages

```{r}
library(pacman)
p_load(
  tidyverse,
  bibliometrix,
  psych,
  stringr
)
```

# Reading data

```{r}
# Reading the selected articles from Rayyan, imported as CSV.
data <- read.csv(file = "Rayyan_export.csv")

# Reading the datasets with all bibliographic data, exported from Scopus and WoS.
# These will be read into a standartized dataframe using bibliometrix, in order to use other bibliometric functions.


scopus <- bibliometrix::convert2df(file = "scopus_metadata.csv", format = "csv", dbsource = "scopus")
wos <- bibliometrix::convert2df(file = "WoS_metadata.txt", format = "plaintext", dbsource = "wos")

# I repurpose the C1 field to retain information about the data source.
wos$C1 <- "wos"
scopus$C1 <- "scopus"

# Scopus has made changes in the export function. Now it allows exporting 20,000 articles. However, they have also changed the title column tag. Bibliometrix cannot handle it, so I manually adjust it.
scopus_colnames <- colnames(scopus)
scopus_colnames[4] <- "TI"

colnames(scopus) <- scopus_colnames


# The mergeDbSources function merges scopus and wos bibliodfs into one. It's basically a bindrows with only matching columns kept.
# However, the result still has the bibliometrix export namespace.
data_merged <- mergeDbSources(scopus, wos, remove.duplicated = FALSE)


```

# Selecting data
The purpose of this section is to filter the  merged bibliometrixdf, so that only our included articles are in it.
Furthermore we always use the information from WoS in case of data being available from both WoS and Scopus, as the entries are more standardized. 

```{r}
# Creating an index for each column in the merged bibliodf. 0 = not included. 1 = included by us.

index <- c()

for (i in 1:nrow(data_merged)) {
  
  if ((data_merged$TI[i] == data$title %>% toupper()) %>% any()) {
    index <- append(index, 1)
  } else {
    index <- append(index, 0)
  }
}

which(index == 1) %>% length()
# ~500 articles have an index of 1, but only ~400 articles are included by us. Therefore, we need to remove duplicates.

# A new dataset, only containing included articles with some duplicates
data_selected <- data_merged[which(index == 1),]


# Loop for removing duplicates: For each included title by us, copy the entry from the bibliometrixdf into a new bibliometrixdf.
# If there are >1 entries in the original bibliometrixdf that match, only write the entry with the "WoS" tag into the new frame.
# If there are >1 matches and none with the "WoS" tag, simply write the first entry into the new frame.

data_selected_deduped <- data.frame()
ids <- c()
for (i in 1:nrow(data)) {
 
  ids <-  which(data$title[i] %>% toupper() == data_merged$TI)


  if (length(ids) > 1) {
  
    if (any(data_merged[ids, "C1"] == "wos")) {
    
      which_wos <- which(data_merged[ids, "C1"] == "wos")
      data_selected_deduped <- rbind(data_selected_deduped, data_merged[ids[which_wos[1]],])
      print(which_wos)
    } else
  
    data_selected_deduped <- rbind(data_selected_deduped, data_merged[ids[1],])
  } else {
    data_selected_deduped <- rbind(data_selected_deduped, data_merged[ids[1],])
  }

}

# Success! Our deduplicated detailed bibliodf contains all the articles we included.
nrow(data_selected_deduped) == nrow(data)

# Saving the results.
# save(data_selected_deduped, file = "merged_bibliodf.Rdata")
```
