# Script for standardizing the Cited References from Scopus and WoS into a new format.

## Load Packages
```{r}
library(pacman)
p_load(
  tidyverse,
  bibliometrix,
  psych,
  stringr,
  reshape2
)
```

## Read Data
```{r}
load("merged_bibliodf.Rdata")

data <- data_selected_deduped
data_selected_deduped <- NULL
```

# Determine Basic Metrics
```{r}
data$C1 %>% table()
# There are almost equal numbers of articles from WoS and Scopus. Formatting is therefore extremely important.

ids_wos <- which(data$C1 == "wos")
ids_scopus <- which(data$C1 == "scopus")

# Getting familiar with the format.

# The format is a standardized and reduced version of APA: included are the first author, the journal has an abbreviation, year, volume, starting page, DOI.
wos_example <- data$CR[ids_wos[1:10]]

# The format is almost the normal APA format.
scopus_example <- data$CR[ids_scopus[1:10]]

# Save examples into variable.
data2 <- data[c(ids_wos[1:4],ids_scopus[1:4]),]

# The WoS format contains less information. As long as the identification of the entries is given, it is more error-free.
# Besides, we cannot transform WoS into Scopus references due to missing information in WoS entries.


# Goal: create a third custom format by merging both.
```

# Information extraction.

Information is extracted from WoS and Scopus entries using regular expression and merged into a new format.

To create a common format the necessary information is based on the content of Web of Science cited references. These include: year, first author, journal (abbreviated), volume, and starting page. If I want to merge Scopus and Web of Science (WoS), the new format can only contain this information because otherwise, WoS CRs would not be transferable. However, I exclude the journals because they can not easily be matched. The other information should be sufficient in our sample to generate fingerprints.

```{r}

# Function for extraction reference Information from Scopus.

extract_scopus <- function(text) {

  # Commas separate information in Scopus references, so the CR text is split at the commas.
  # This creates a character vector. Generally, the first element is the first author, and the last element is the year.
  split_content <- str_split(pattern = ",", string = text) %>% unlist()
  
  split_content <- trimws(split_content)
  
  # If the vector contains 2 or fewer elements, it means that at least two pieces of information about year, title, or first author are missing.
  # These pieces of information are essential, so the function refuses to extract information in these cases and returns "Na".
  if (length(split_content) < 3) {
    return(c("Na", "Na", "Na", "Na"))
  }
  
  ## Author
  # The first element is always the first author. If it is missing, the title is used as a substitute.
  # Remove whitespace at the beginning.
  # Remove periods after the initials, and store the result.
  
  split_content[1] <- trimws(split_content[1])
  
  first_author <- split_content[1] %>% str_extract(pattern = "^[\\w-]+\\W+(\\w{1})")
  
  if (is.na(first_author)) {
    first_author <- split_content[1] %>% str_extract(pattern = "^[\\w-]+")
  }
  
  ## Year
  # The year is always the last element. The function is designed to consider only entries with a year.
  # Peer-reviewed literature should always have a year.
  # Transform the year: remove "()" and keep only 4-digit numbers using regex (e.g., 2022).
  
  year <- split_content[length(split_content)] %>% gsub(pattern = "\\(|\\)|\\s", replacement = "")
  year <- year %>% str_extract(pattern = "\\d{4}")
  
  ## Volume
  # The volume is usually an element that contains a 1-3 digit number.
  # It is at position -3 in the vector if there is a page number. Otherwise, it is at position -2:
  # E1, E2, Ei, *Volume*, Page, Year
  
  # Store the element numbers of all elements that contain a number: possibly title, volume, page, year
  digit_cols <- which(grepl(split_content, pattern = "\\d"))
  
  # If either of the last two elements contains "PP" followed by any number of digits, there is a page reference.
  # In that case, the volume, if available, should exist before the second-to-last element with "PP" (indicating a page reference).
  # This position is stored temporarily. Parentheses and whitespace are removed.
  # If the element before the page reference does not contain numbers, there is no volume in the string.
  
  if (any(grepl(split_content[(length(split_content)-2):length(split_content)], pattern = "^PP\\..*\\d+"))) {
    page_cols <- max(grep(split_content, pattern = "PP."))
    volume_id <- page_cols - 1
    
    if (volume_id %in% digit_cols) {
      volume <- split_content[volume_id] %>% gsub(pattern = "\\(|\\)|\\s", replacement = "")
    } else {
      volume <- "noVolume"
    }
  
    # If there is no page reference with "PP": Find out if the second-to-last and third-to-last elements contain numbers.
    # In that case, they could be a wrongly formatted page number and the volume.
    # In that case, the volume is the last element with a number before the page and the year. (One could also simply choose the element -3.)
  } else {
    if ((length(split_content) - 1) %in% digit_cols & (length(split_content) - 2) %in% digit_cols) {
      volume_id <- digit_cols[which.max(which(digit_cols < (length(split_content) - 1)))]
      volume <- split_content[volume_id] %>% gsub(pattern = "\\(|\\)|\\s", replacement = "")
      
      # If the above condition is not met: Are there two elements with numbers in the last two elements? Then it could be year & page or year         & volume.
      # Volume & page cannot always be clearly distinguished since both can simply be a digit.
      # Therefore, here we simply choose the last number element before the year.
      
  
      
      # If there is only one digit, it definitely has no volume and page --> enter "noVolume".
    } else {
      if ((length(split_content) - 1) %in% digit_cols) {
        volume_id <- digit_cols[which.max(which(digit_cols < length(split_content)))]
        volume <- split_content[volume_id] %>% gsub(pattern = "\\(|\\)|\\s", replacement = "")
      } else {
        volume <- "noVolume"
      }
    }
  }
  
  ## Page
  # The page is usually contained in element -2. It typically follows the format "PP." "Starting digits" "-" "Ending digits".
  # Sometimes, it can be just a number without the other characters, making it difficult to distinguish from the volume.
  
  # Is there an element in the last three elements that matches the standard format? If so, extract and store the starting page.
  if(any(grepl(split_content[(length(split_content)-1)],pattern = "^PP."))){

  starting_page <- split_content[length(split_content)-1]%>%str_extract(pattern = "\\d+")

}else{
  
  
  if((length(split_content)-1)%in% digit_cols&(length(split_content)-2)%in% digit_cols){
    starting_page <- split_content[length(split_content)-1]%>%
      str_extract(pattern = "\\d+")
    
  }else{
    # If that's not the case: no page!
    starting_page <- "noPage"
  }
}

# Volumes are often incorrectly extracted. So here are a few checks:
# 1. Remove "." and everything between "V" and "volume".
#    Only digits < 2024 should remain. The oldest English journal has a volume of 371.
#    https://en.wikipedia.org/wiki/Philosophical_Transactions_of_the_Royal_Society 
#    De Gruyter Journal sometimes uses the year as the volume.

volume <- sub(volume,pattern = "\\.",replacement = "",ignore.case = TRUE)
volume <- sub(volume,pattern = "\\bv\\D{0,6}",replacement = "",ignore.case = TRUE)

if(grepl(volume,pattern="(?=\\D)(?=\\S)",perl = TRUE)){
  volume <- "noVolume"
}

# Extract the largest number occurring in the volume statement.
volume_number <- (str_extract_all(volume,"\\d+")%>%unlist())[which.max(str_extract_all(volume,"\\d+")%>%unlist())]

# Is it >2023? <-- Then it's noVolume
if(!length(as.numeric(volume_number))==0){
  if(as.numeric(volume_number)>2023){
    volume <- "noVolume"
  }
}

# Remove whitespace and return the result.
return(trimws(c(year,volume,starting_page,first_author)))
}

```

# Create a function that generates a custom format from the extracted information.
# Very basic. Take all the information, separate them by *,*, and paste them together.

```{R}
# See function description.
create_cus_format <- function(year, volume, starting_page, first_author){
  
  entry <- paste(first_author, year, volume, starting_page, sep = ", ")
  
  return(entry)  
}
```

```{r}
# Create a function that extracts information about the first author, publication year, starting page and volume using Regular expression.


extract_wos <- function(text){

# Split the content elements by comma into a vector.
split_content <- text %>% strsplit(split = ",")%>%unlist()
split_content <- trimws(split_content)

##Author
# The first author is always at position 1. If it's missing, then the title is used as a replacement.
# Here, the first word (last name) is combined with the initials of the second word.
# If the initials are missing, only the first word is used.
# Also, remove whitespace at the beginning.

split_content[1] <- trimws(split_content[1])

author <- split_content[1]%>%str_extract(pattern = "^[\\w-]+\\W+(\\w{1})")

if(is.na(author)){
author <- split_content[1]%>%str_extract(pattern = "^[\\w-]+")}


##Year
# The year is always at position 2. This function only applies to articles with a valid year.

year <- split_content[2]%>%gsub(pattern = "\\s*","")

##Volume
# If there is a column with a "V" followed by several digits, then it's the volume.
# The title is not included, so there can be no misunderstandings.
# Only the number of the volume is stored.

if(any(grepl(split_content,pattern = "^V\\d+"))){
volume_id <- min(grep(split_content,pattern = "\\bV\\d+"))
volume <- gsub(split_content[volume_id],pattern = "V",replacement = "")
}else{
  
# If that's not the case: noVolume
volume <- "noVolume"
}

# Check volume data:

volume <- sub(volume,pattern = "\\.",replacement = "",ignore.case = TRUE)
volume <- sub(volume,pattern = "\\bv\\D{0,6}",replacement = "",ignore.case = TRUE)

if(grepl(volume,pattern="(?=\\D)(?=\\S)",perl = TRUE)){
  volume <- "noVolume"
}

# Extract the largest number occurring in the volume information.
volume_number <- (str_extract_all(volume,"\\d+")%>%unlist())[which.max(str_extract_all(volume,"\\d+")%>%unlist())]

# If this number is >2023, then noVolume
if(!length(as.numeric(volume_number))==0){
if(as.numeric(volume_number)>2023){
  volume <- "noVolume"
}}





##Page
# Each content record that has a field starting with "P" is followed by numbers contains a starting_page.
# It is stored as starting_page.
if(any(grepl(split_content,pattern = "^P\\d+"))){
page_id <- min(grep(split_content,pattern = "^P\\d+"))
starting_page <- str_extract(split_content[page_id],pattern = "\\d+")
}else{
  
# If that's not the case: noPage
starting_page <- "noPage"
}

# The obtained information is returned as a vector,
# after removing leading and trailing whitespace.
return(trimws(c(year,volume,starting_page,author)))
}

```
# Looping thorugh the data, unsing the defined functions to extract information.
## If volume and page are missing the entry is skipped.
## The same apllies if the publication year is missing.

```{r}
# Create a new, empty column for the new references.
data_streng <- data
data_streng$CR_new <- 0

# For each article:
for(i in 1:nrow(data_streng)){
  
  # Extract and split the references.
  crs <- strsplit(data_streng$CR[i], split = ";") %>% unlist()
  
  # If no references are present, skip.
  if(!any(!is.na(crs))){
    next
  }
  
  # Mark those that do not contain a date, depending on the WoS or Scopus format.
  if(data$C1[i] == "wos"){
    contains_date <- grepl(crs, pattern = " \\d{4},")
  } else{
    contains_date <- grepl(crs, pattern = "\\(\\d{4}\\)")
  }
  
  crs_no_date <- crs[!contains_date]
  crs_date <- crs[contains_date]
  
  if(data$C1[i] == "wos"){
    crs_extracted <- sapply(crs_date, extract_wos) %>% t()
  } else{
    crs_extracted <- sapply(crs_date, extract_scopus) %>% t()
  }
  
  tmp_vec <- c()
  for(z in 1:nrow(crs_extracted)){
   
   ## validate results
   
   values <- crs_extracted[z,] %>% c()
   values <- trimws(values)
   
   # Missing author or NA excluded. Otherwise, it will be skipped.
   if(is.na(values[4]) | values[4] == "ANONYMOUS" | values[4] == "Na" | values[4] == ""){
     next
   } else if(grepl(values[4], pattern = "\\d")){
     next
   } else if(grepl(values[4], pattern = "^\\w+")){
     
     if(nchar(str_extract(values[4], pattern = "^\\w+")) <= 1){
       next
     }
   } else{
     next
   }
   
   # Year must be >1665 & <2024. Otherwise, it will be skipped.
   if(is.na(values[1]) | values[1] == "") {
      next
   } else if(!grepl(values[1], pattern = "\\D+")) {
      if(as.numeric(values[1]) < 1665 | as.numeric(values[1]) > 2023){
         next
      }
   }
   
   # Page numbers can only contain digits.
   if(grepl(values[3], pattern = "\\D+")){
     values[3] <- "noPage"
   }
   
   # Remove leading zeros.
   # Page
   values[3] <- sub(values[3], pattern = "^0", replacement = "")
   
   # Volume
   values[2] <- sub(values[2], pattern = "^0", replacement = "")
   
   if(is.na(values[3])){
     values[3] <- "noPage"
   }
   
   if(values[2] == "noVolume" & values[3] == "noPage"){
     next
   }
   # Create the new formate for the reference and append it to the articles new references.
   tmp_vec <- append(tmp_vec, create_cus_format(year = values[1], volume = values[2], starting_page = values[3], first_author = values[4]))

   if(is.na(values[4])){
     cat(i)
   }
 }
 
# Stich togehter the refernce vector using ";" as a seperator.
crs_new <- paste(tmp_vec, collapse = ";")

 data_streng$CR_new[i] <- crs_new
}

```

# Check the Resuluts

```{r}
# Unlist reference string
crs_new_sep_streng <- data_streng$CR_new%>%str_split(pattern = ";")%>%unlist()

which(crs_new_sep_streng==0)

# No missing values
nas <- grepl(pattern = "Na,",crs_new_sep_streng)

length(which(nas))/length(crs_new_sep_streng)


noPages <- grepl(pattern = "noPage",crs_new_sep_streng)

length(which(noPages))/length(crs_new_sep_streng)
# 10.26% have no page indication

noVolume <- grepl(pattern = "noVolume",crs_new_sep_streng)

length(which(noVolume))/length(crs_new_sep_streng)
# 28.09% have no volume indication



length(which(noPages&noVolume))/length(crs_new_sep_streng)
# 0


cr_sample_streng <- crs_new_sep_streng

matches <- (length(which(table(cr_sample_streng)>=2))/length(crs_new_sep_streng))*100
# 7.76%
```

# Save the results

```{r}
#save(data_streng, file="data_new_crs.Rdata")
```

